\documentclass[12pt,titlepage]{article}
\input{settings}

\begin{document}
\include{cover}

\maketitle
\newpage
\tableofcontents
\thispagestyle{empty}
\setcounter{page}{0}
\newpage

\section{Introduction}
\subsection{References}
\subsection{Purpose}
This document describes the requirements and functionalities of the "Bicycle Garage Pro" (BGP) software.

The intended audience of this document are mainly: software developers, in order to aid the development of the software; and clients, in order to provide an accurate overview of the project.
\subsection{Glossary}
\begin{enumerate}
	\item Business-related terms
	\begin{enumerate}
		\item BGP - Bicycle Garage Pro (software)
		\item ACME - The company which BGP is produced for
	\end{enumerate}

	\item Product-related terms
	\begin{enumerate}
	\item System - Bicycle Garage Pro software
	\item PIN - Four-digit code, used to access the garage
	\item API - Application programming interface
	\item Entrance - Main entrance door of the garage
	\item User - Cyclist who uses the Bicycle Garage Pro system
	\item Exit 1 - Garage exit for users with bicycles
	\item Exit 2 - Garage exit for users without bicycles
	\item Operator - Subject responsible for managing BGP (on-site)
	\end{enumerate}
\end{enumerate}

\subsection{Scope}
BGP is a software application that manages a bicycle garage. This requirement specification only covers the software part for the bicycle garage and the following assumptions are therefore made about the hardware:
\begin{enumerate}
	\item The hardware handles recognition and reading (scanning) of barcodes
	\item The hardware handles printing of barcodes
	\item The hardware handles locking and unlocking of doors
	\item The hardware handles reading of PINs
\end{enumerate}
The hardware, as stated above, will be accessed by the system according to a predefined API. See \cref{app:hardware} for a more detailed description of the API.

\subsection{Goals}
\subsubsection{Business goals}
ACME is a company that works in the bicycle garage business. ACME aims to provide low-cost, semi-automated bicycle garage solutions for public use.
\subsubsection{Product goals}
The goal of BGP is to assist in managing a bicycle garage by keeping track of users and their bicycles. The user interface should be simple to use and the software should be easily maintainable for future developers.
\subsection{Overview}


\include{appendix}
\end{document}